### 2023-10-04 3.Design/dataset.tex
Few more words ...
Updates on dataset

@@

The values for the data

>>>>

\subsection{Airline}

The first dataset is very simple and was mostly used to check whether the analog circuit was working. It is extracted from the tutorial available at \cite{airline}. The dataset is available at \cite{datasets}, the name of the file containing the dataset is \textit{airline-passengers.csv}.

This is a regression problem, meaning that the point is to predict the number of passenger of the next month

\begin{figure}[H]
\centering
\includesvg[width=\textwidth]{datasets/airline}
\caption{Graphical representation of the airline passenger dataset. The vertical lines represent a full year.}
\label{fig:afGraph}
\end{figure}

@@

The values for the data needs to be set not to exceed 1. This is to make sure that the terminal voltage doesn't reach the threshold as explained in \cref{sec:xbarCircuit}.
